### 2013-09-23 evaluation/paper.tex
more figures in evaluation.

The results for the OCR-large dataset are shown in \figref{ocr_large_results}
The trends are the same as for the smaller dataset: $n$-slack and caching $1$-slack cutting plane are very fast
in terms of passes through the dataset, but $n$-slack cutting plane is impractical slow
with respect to runtime. The SZLJSP algorithm converges fast intially, but the $1$-slack cutting plane
is faster at high precision and faster in certifying the desired duality gap.

>>>>

The results for the OCR-large dataset are shown in \Figref{ocr_large_results}
The trends are the same as for the smaller dataset: $n$-slack and caching $1$-slack cutting plane are very fast
in terms of passes through the dataset, but $n$-slack cutting plane is impractical slow
with respect to runtime. The SZLJSP algorithm converges fast intially, but the $1$-slack cutting plane
is faster at high precision and faster in certifying the desired duality gap.
%TODO initially 1-slack is beaten by ssgd
\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{evaluation/images/yeast_tree}&%
    \includegraphics[width=\linewidth]{evaluation/images/yeast_tree_time}
    \end{tabu}
\caption{%
   Convergence of the primal objective on the multi-label yeast dataset with a tree-shaped model.
\figlabel{yeast_tree}}
\end{figure}

\begin{figure}
    \begin{tabu} to \linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{evaluation/images/scene_tree}&%
    \includegraphics[width=\linewidth]{evaluation/images/scene_tree_time}
    \end{tabu}
\caption{%
   Convergence of the primal objective on the multi-label scene dataset with a tree-shaped model.
   \figlabel{scene_tree}}
\end{figure}

Next, we consider the multi-label task, starting with the tree-shaped models.
The results for the yeast and scene datasets are shown in \Figref{yeast_tree} and \Figref{scene_tree},
respectively. The caching $1$-slack algorithm is much faster than the non-caching one on both datasets.
The caching $1$-slack algorithm is the fastest algorithm to achieve the desired primal suboptimality.
On the scene dataset, the other cutting-plane base algorithms are second fastest, while they
lag behind the stoachastic algorithms on the larger yeast dataset. Again, initial convergence is
faster for the stochastic algorithms.

The results when using the full model are shown in \Figref{yeast_full} and \Figref{scene_full}.
Here, inference is much more complex than in the previous tasks.
